Testing the Fidelity of Simulations of Black Hole -- Galaxy Coevolution

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/manuscript_before_John_edit/manuscript.tex
Galight example, HSC online fitting, simulation paper updates

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}

@@

\begin{document}

\title{The Black Hole and Galaxy coevolution at $0.2<z<1.7$ using extensive comparisons between observation and simulation}

@@

\author[0000-0002-1605-915X]{Junyao Li}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
\affiliation{CAS Key Laboratory for Research in Galaxies and Cosmology, Department of Astronomy, University of Science and Technology of China, Hefei 230026, China}
\affiliation{School of Astronomy and Space Science, University of Science and Technology of China, Hefei 230026, China}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
We carry out a direct comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh -- \smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN,  TNG and semianalytic model). The observational measurements consistent of 612 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter. To make the fair comparisons, we first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as that based on observations. Our analysis demonstrates that all simulations predict a comparable level of dispersion of the scaling relations up to $z\sim1.7$, even after consideration of observational uncertainties which are non-negligible. 
%We also find that the selection criteria for the $z<1$ do not produce strong effects on the simulated relation
%Thus, the original relations (i.e., before adding noise) predicted by the simulation are supposed to have consistent intrinsic scatter compared with the observational data. 
%Considering that the tight relation of the scaling relation is highly rely on the AGN feedback, our results support the hypothesis of the AGN feedback being responsible for a causal link between the BH and its host galaxy, resulting in a tight correlation between their respective masses.
Hence, our results support the hypothesis that AGN feedback plays a role in a causal link between the BH and its host galaxy, resulting in a non-evolving and tight correlation between their respective masses. 
\todo{Mentioning the central comparison.}

%\todo{Add comments on the center positions. KS test. Estimation of the intrinsic scatter.}
\end{abstract}
\keywords{Galaxy evolution (594); Active galaxies (17); Active galactic nuclei (16)}

\section{Introduction} \label{sec:intro}
The close correlations between supermassive black holes and the properties of their host galaxies (e.g., stellar mass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determin how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}. While, an {\it apparent} evolution has been found in which the growth of BHs predates that of the host, equally as many studies claim a lack of evolution when considering the host total stellar mass. However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014}.

Various theoretical models have been proposed to explain the origin of the scaling relations. For example, AGN feedback is considered as one of the possible viable mechanisms. During this process, a fraction of the AGN energy is injected into its surrounding gas, which can then regulate the mass growth of the BH and its host. In this scenario, star formation is inhibited by the heating and unbinding of a significant amount of gas. Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common gas supply~\citep{Cen2015, Menci2016}. Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}. However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ as observed today.

Numerical simulations provide an opportunity to further understand the origin of the connection between BHs and their host galaxies. For example, a comparison of scaling relations has been made between predictions by the state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ based on HST imaging \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH growth predates that of its host). Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution, including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments suite of SPH simulations~\citep{Schaye2015}, Illustris moving-mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019} and the SIMBA simulation~\citep{Thomas2019}. In recent work, the BH populations from the six large-scale cosmological simulations have been adopted to compare the \mbh-\smass\ with observation of the local universe~\citep{Habouzit2021}. However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range ($z<1$).

For such comparisons using simulations, it is crucial to consider the systematic uncertainties and selection biases. A direct means to account for these is to apply the same effects and selection to the simulation products and make a forward comparison in the observational plane. In~\citet{Ding2020b}, a direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and a direct comparison with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and a Semianalytic Model (SAM). The dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) confirming the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.

In this study, we extend our previous work, comparing the observational measurements to that from simulations, by adding recent measurements of hundreds of SDSS quasar at $0.2<z<0.8$ based on wide and deep HSC imaging from the Strategic Subaru Program. Furthermore, we extend the simulated quasar populations by including MBII, SAM, Illustris, TNG100, TNG300 and Horizon-AGN. This paper is structured as follows. In Sections~\ref{sec:observations} and~\ref{sec:simulations}, we describe our observation and simulation sample. The direct comparison is performed and the result is presented in Section~\ref{sec:result}. The concluding remarks are presented in Section~\ref{sec:con}.

%\section{Comparison Sample: Observations and Simulations} \label{sec:sample}
%The correlations of \mbh-\smass\ between the observed data and the numerical simulations are compared in this work. 
%We introduce the comparison samples in this section, including the observational data and the numerical simulations.

\section{Observational data set}
\label{sec:observations}
The observed sample consists of 900 uniformly-selected SDSS quasars at $0.2<z<0.8$, imaged by Subaru/HSC \citep{Li2021a}, and 32 quasars at $1.2<z<1.7$ as imaged by~\hst and described in \citep[][hereafter D20]{Ding2020}. The latter are selected from three deep-survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008}. Further details of these two samples and their measurements are given below.

\subsection{HSC}\label{sec:hsc}
A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}. With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been performed \citep[][hereafter L21a]{Li2021a} to obtain the flux and color of each quasar's host galaxy. The stare-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task. This approach is first developed by~\citet{Ding2020} and used to decompose the near-infrared emission of the HST sample (see next section). Having measured the host light in each band, the stellar mass of host galaxy is derived using spectral energy distribution (SED) fitting with CIGALE~\citep{Boquien2019}. Simulation tests are also performed to verify the fidelity of the \smass\ measurements. The statistical measurement error on \smass\ is at the $\sim$0.2~dex level. The values of \mbh\ are determined by~\citet{Rakshit2020} which are estimated based on the \hbeta-based measurements using the virial method~\citep{Peterson2004, Vestergaard2006}. The typical error of \mbh\ are estimated to be 0.4 dex. We refer the reader to~\citet{Li2021a} in the Section~4.2 for more details.

To avoid any potential biases related to the selection of the quasars, \citet[][hereafter, L21b]{2021arXiv210902751L} isolated 877 sources which are uniformly selected based on their PSF-magnitudes, color cuts using single-epoch SDSS photometry and the value of the measured \smass. Specifically, we use the {\it ugri} color-selected sample (228 sources) from SDSS I/II~\citep{Richards2002}, and the CORE sample from SDSS BOSS (408 sources) and eBOSS (241 sources) surveys~\citep{Ross2013, Myers2015} (hereafter the uniform sample). These samples are initially selected based on PSF-magnitude cuts of $15 < i < 19.1$ (for {\it ugri}), and $i > 17.8$ and $g, r < 22.0$ (for CORE). Finally, a limit on \smass\ is set to assure the detection of the host, especially since the rate and accuracy of detection is higher when \smass\ is increasing. These selections will be adopted in an equivalent manner to the simulated samples to mitigate selection effects thus allowing the fair comparison.

\subsection{HST}

A sample of 32 HST-observed AGN systems across the redshift range $1.2<z<1.7$ are selected from three deep-survey fields (COSMOS, (E)-CDFS-S, and SXDS). HSC/WFC3 IR camera is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six position dither pattern and a total exposure time $\sim$2348~s. The filters F125W ($1.2<z<1.44$) and F140W ($1.44<z<1.7$) were employed, according to the redshift of each target to bracket the 4000~\AA~break.  The AGN images are analyzed and decomposed to infer the host galaxies fluxes using the approach developed by D20 based on {\tt lenstronomy}. The HST ACS/F814W imaging data for 21/32 of the AGNs is also used to infer the host color. The results show that stellar templates of 1 and 0.625~Gyr can match the sample color at $z<1.44$ and $z>1.44$, respectively (see Figure 5 in D20). These best-fit models are used to estimate the stellar masses of the host galaxies. \mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citep{Vestergaard2006}, in a consistent manner to that adopted for HSC sample. We refer the reader to D20 for a more detailed description of the analysis.

With a consistent approach, the measurements of the \mbh-\smass\ relations for the HST and HSC samples are obtained. Thus, we expect the measurement errors of these two samples to be at a comparable level (i.e., $\Delta$\mbh$=0.4~$dex, $\Delta$\smass$=0.2~$dex). 
Indeed, the two samples are consistent with a lack of evolution in the mass ratio (see Figure 6 of L20b), even though the sample selection is slightly different.

\section{Simulations}
\label{sec:simulations}
We introduce the simulation sample that adopted in this section. All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation.
%\todo{Maybe we can also summarize the importance of AGN feedback somewhere here?}

\subsection{{\tt MassiveBlackII} (MBII)}
MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles. The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}. For dark matter and gas, the elements of the masses resolution are $1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$, respectively. The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process. Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}. Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}. The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}, i.e., $\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.

@@

\subsection{Semianalytic Model (SAM)}
We highlight here the main points of the simulation with respect to our study; for more detail, a full descriptions of the SAM simulation sample can be found in~\citet{Menci2016} which is based on semianalytic model introduced in~\citet{Menci2014}. For dark matter halos that merge with a larger halo, the impact of dynamical friction is assessed to define whether the halo will survive as a satellite or sink to the center of the dominant galaxy to increase its mass. The binary interactions (fly-by and merging), among satellite subhalos, are  also described by the model. In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}. The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulating star formation (as well as BH accretion). The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase. A Salpeter IMF is adopted in the SAM simulation.

@@

\subsection{Illustris}
The Illustris Project is a serise of larger-scale hydrodynamical simulations of galaxy formation which was introduced in~\citet{2014MNRAS.444.1518V, 2014Natur.509..177V}. The simulation consist of a volume of (106.5 cMpc)$^3$, and was run with the moving Voronoi mesh code {\tt Arepo}~\citep{2010MNRAS.401..791S}. Besides gravitational force and hydrodynamical fluxes, the simulation calculates the astrophysical process known to be crucial for galaxy formation~\citep{2013MNRAS.436.3031V, 2014MNRAS.438.1985T}, which includes gas cooling, a subresolution ISM model, stochastic SF with a density threshold of 0.13 cm$^{-3}$, stellar evolution, gas recycling, chemical enrichment, kinetic stellar feedback by SNe activity, BH activity (accretion and merging), and AGN feedback. A cosmological background consistent with WMAP9~\citep{2013ApJS..208...19H} and a Chabrier IMF is adopted.

@@

\subsection{IllustrisTNG}
{\it The Next Generation Illustris Simulations} (IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018} are an ambitious suite of hydrodynamical simulations of galaxy formation in large cosmological volumes. It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modelling, and 3) addressing the identified shortcomings of the previous generation simulations.

@@

\subsection{Horizon-AGN}
The simulation of Horizon-AGN~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D} has a volume of (142 cMpc)$^3$ which was generated based on the adaptive mesh refinement code {\tt Ramses}~\citep{2002A&A...385..337T} with a $\Lambda$CDM model based on WMAP7~\citep{2011ApJS..192...18K} cosmological results. The total volume contains $1024^3$ DM particles, corresponding to a DM mass resolution of $8 \times 10^7  M_{\odot}$  and initial gas resolution of  $1\times10^7M_{\odot}$. A Salpeter IMF is assumed in Horizon-AGN simulation.

@@

We summarized some key elements in the simulation in Table~\ref{tab:sim_sum}.

\begin{deluxetable*}{lcccccc}
%\tablenum{1}
\tablecaption{Summary of some key assumptions for the hydrodynamic simulations analyzed by this work.\label{tab:sim_sum}}
\tablewidth{0pt}
\tablehead{
%\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
%  \cline{2-4}  \cline{5} \\
\colhead{Simulation} & \colhead{box sizes} & particles &  \colhead{resolution} & \colhead{feedback prescription} & \colhead{AGN fueling mechanism}  & what else?
}
\startdata
%SAM & \\
MBII & $100~\mathrm{cMpc/h}$ & $2\times1792^3$ &&& \\
Illustris &&&&& \\
TNG100 &&&&& \\
TNG300 &&&&& \\
Horizon-AGN &&&&& \\
\enddata
%\tablecomments{This table }
\end{deluxetable*}

\subsection{Application of observational selection effects}
To make direct comparisons with observations, we add measurement errors and apply the equivalent selection to the simulated samples. We first inject random noise to the simulated catalog to mimic the scatter caused by the measurement error. As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach thus their uncertainty levels are expected to be equivalent. 
We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.17~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.

We then apply restrictions on the noise-injected simulation to mimic selection effects as present in the observational data. Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows.
\begin{itemize}

>>>>

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}

@@

\begin{document}
\title{Testing the Fidelity of Simulations of Black Hole -- Galaxy Coevolution}

@@

\author[0000-0002-1605-915X]{Junyao Li}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
We investigate the evolution of the scaling relations between the supermassive black hole (BH) and its host galaxy stellar mass (\smass-\mbh) by making comparisons between observations and simulations at $0.2<z<1.7$. The measurements of the observational data are consistent of 612 uniformly-selected SDSS quasars at $0.2 < z < 0.8$ that imaged by Hyper Suprime-Cam (HSC) and 32 X-ray-selected, broad-line AGNs imaged by the Hubble Space telescope (HST) at $1.2<z<1.7$. We make direct comparisons by first adding realistic observational error to the simulation data and then making selection to the sample follows real observation condition. Our results show that all the simulations predict consistent scatter of the scaling relations to both HSC and HST sample, across board redshift range. %We also find that the selection criteria for the $z<1$ do not produce strong effects on the simulated relation. 
The scatter of the scaling relation is dominated by the observational error. Thus, the original relations (i.e., before adding noise) predicted by the simulation are supposed to have consistent intrinsic scatter compared with the observational data. Considering that the tight relation of the scaling relation is highly relay on the AGN feedback, our results support the hypothesis of the AGN feedback being responsible for a causal link between the BH and its host galaxy, resulting in a tight correlation between their respective masses.
%\todo{Add comments on the center positions. KS test. Estimation of the intrinsic scatter.}
\end{abstract}
\keywords{Galaxy evolution (594); Active galaxies (17); Active galactic nuclei (16)}

\section{Introduction} \label{sec:intro}
The close correlations between the supermassive black holes and their host galaxies properties (stellar mass in particular) indicates a physical coupling during their coevolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused to measure the correlation using board-line active galactic nucleus (AGN) to measure them as a function of redshift, intending to see how and when the correlation emerge and evolve over cosmic time \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}. While, an {\it apparent} evolution has been found in which the growth of BHs predates that of the host, equally as many studies claim a non-evolution when considering the host total stellar mass. To understand the significance {\it intrinsic} evolution, it is important to take into account the systematic uncertainty of the measurement and the selection effect~\citep{Tre++07, Lauer2007, Schulze2014}.

In theory, various models have been proposed to explain the origin of the scaling relation. For instance, the AGN feedback is considered as one of the possible physical link. During this process, the fraction of the AGN energy is injected into its surrounding gas, which regulates the mass growth of the BH and its host. In this scene, the star formation is inhibited by the heating and unbinding of a significant fraction of the gas by the AGN activity. Alternatively, the scaling relation can be explained through a more indirect connection in which AGN accretion and host star formation are fed through a common gas supply~\citep{Cen2015, Menci2016}. Without any physical mechanisms, the statistical convergence from galaxy assembly alone (i.e., dry mergers) could regulate the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}. From this central limit theorem, higher dispersion would appear in the scaling relations at high-$z$ as observed today.

Numerical simulation provides good opportunity to understand the origin of the connection. For example, the comparison of the scaling relations has been made between the predictions by the state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and the HST observational measurements at  $0.3<z<1$, which show a positive evolution that BH growth predates than its host~\citep{DeG++15}. The efforts have been taking to use large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution, including the Magneticum Pathfinder smooth particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments suite of SPH simulations~\citep{Schaye2015}, Illustris moving mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019} and SIMBA simulation~\citep{Thomas2019}. In recent work, the BH populations from the six large scale cosmological simulations have been adopted to compare the \mbh-\smass\ with observation of the local universe~\citep{Habouzit2021}. However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and the redshift range ($z<1$).

In the meanwhile, it is crucial to consider the systematic uncertainties and selection biases in the comparison. A direct way to take them in to account is to apply the same effects to the simulation products and make a forward comparison in the observational plane. 
In~\citet{Ding2020b}, this direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and direct compare with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and Semianalytic Model (SAM). The dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) confirming the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.

In this study, we extend our previous comparison work by adding the latest measurements of hundreds SDSS quasar $0.2<z<0.8$ using the latest HSC observation. We adopt more simulated quasar populations including MBII, SAM, Illustris, TNG100, TNG300 and Horizon. This paper is structured as follows. In section~\ref{sec:sample}, we describe our observation and simulation sample. The direct comparison is performed and the result is presented in section~\ref{sec:result}. The concluding remarks are presented in section~\ref{sec:con}.

\section{Comparison Sample: Observations and Simulations} \label{sec:sample}
%The correlations of \mbh-\smass\ between the observed data and the numerical simulations are compared in this work. 
We introduce the comparison samples in this section, including the observational data and the numerical simulations.

\subsection{Observation Data}
The observational data are consistent of 900 HSC-observed uniformly-selected SDSS quasars at $0.2<z<0.8$~\citep{Li2021a} and 32 \hst-observed quasars analyzed in \citep[][hereafter D20]{Ding2020} which are selected from three deep-survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008}. The details of the observational data and their measurements are introduced in following subsections.

\subsubsection{HSC}\label{sec:hsc}
A sample of $\sim$5000 type-1 SDSS DR14 quasar catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged through high-resolution Subaru Strategic Program (SSP) wide survey~\citep{Aihara2019} by Hyper Suprime-Cam~\citep{Miyazaki2018}. With accurate PSF model and {\it grizy} bands, the two-dimensional quasar-host decomposition has been performed in~\citet[][hereafter L21a]{Li2021a} to obtain the quasar host galaxies flux and the color. The stare-of-the-art image modeling software {\tt lenstronomy}\citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task. This approach is first developed by~\citet{Ding2020}, which is used to decompose the HST sample (see next section). Having inferred the host light, the stellar mass of host galaxy is derived using spectral energy distribution (SED) fitting by CIGALE~\citep{Boquien2019}. A simulation tests are also performed to verify fidelity of the \smass\ measurements. The measurement error of \smass\ is dominated by the Spectral Energy Distribution (SED) fitting which is at a 0.2~dex level. The \mbh\ are taken from~\citet{Rakshit2020} which are estimated by the \hbeta-based measurements using virial method~\citep{Peterson2004, Vestergaard2006}. The typical error of \mbh\ are estimated to be 0.4 dex. We refer the reader to~\citet{Li2021a} in the Section~4.2 for more details.

To avoid any potential biases related to the selection of the quasars, \citet[][hereafter, L21b]{2021arXiv210902751L} adopted the 877 sources which are uniformly selected based on PSF-magnitude, color cuts using single-epoch SDSS photometries and the value of the measured \smass. Specifically, we use the {\it ugri} color-selected sample (228 sources) from SDSS I/II~\citep{Richards2002}, and the CORE sample from SDSS BOSS (408 sources) and eBOSS (241 sources) surveys~\citep{Ross2013, Myers2015} (hereafter the uniform sample). These samples are initially selected based on PSF-magnitude cuts of $15 < i < 19.1$ (for {\it ugri}) and $i > 17.8 \& g/r < 22.0$ (for CORE). Finally, considering that the accuracy of the measured \smass\ is higher when \smass\ is increasing, a cut on \smass\ is set to assure the measurement accuracy. These selections will be adopted to the simulation sample to erase the selection effect and allow the fair comparison.

\subsubsection{HST}
A sample of 32 HST-observed AGN systems across the redshift range $1.2<z<1.7$ are selected from three deep-survey fields (COSMOS, (E)-CDFS-S, and SXDS). HSC/WFC3 is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six dither pattern and a total exposure time $\sim$2348~s. The filters F125W ($1.2<z<1.44$) and F140W ($1.44<z<1.7$) were employed, according to the redshift of each target.  The AGN images are analyzed and decomposed to infer the host galaxies fluxes using the approached developed by D20 based on {\tt lenstronomy}. The HST ACS/F814W imaging data for 21/32 of the AGNs is also used to infer the host color. The results show that the 1 and 0.625~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$, respectively (see Figure 5 in D20), which are adopted to estimate the stellar masses of the host galaxies. We refer the interested reader to D20 for more detailed description. 
The \mbh\ is determined using published near-infrared spectroscopic observations of the broad \halpha\ emission line with recipe provided by~\citep{Vestergaard2006}, the recipe is consistent with the one adopted by HSC sample \mbh.

Based on the consistent approach, the measurements of the \mbh-\smass\ relations for the HST sample and the HSC sample are obtained. Thus, we expect the measurement error of these two samples to be at the same level (i.e., $\Delta$\mbh$=0.4~$dex, $\Delta$\smass$=0.2~$dex). 
Indeed, the HST and HSC sample demonstrate consistent evolution distribution in L20b Figure 6, though the sample selection is slightly different.

\subsection{Simulation}
We introduce the simulation sample that adopted in this section. All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation.
%\todo{Maybe we can also summarize the importance of AGN feedback somewhere here?}

\subsubsection{{\tt MassiveBlackII} (MBII)}
MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles. The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}. For dark matter and gas, the elements of the masses resolution are $1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$, respectively. The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process. Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}. Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}. The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}, i.e., $\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.

@@

\subsubsection{Semianalytic Model (SAM)}
We highlight here the main points of the simulation with respect to our study; for more detail, a full descriptions of the SAM simulation sample can be found in~\citet{Menci2016} which is based on semianalytic model introduced in~\citet{Menci2014}. For dark matter halos that merge with a larger halo, the impact of dynamical friction is assessed to define whether the halo will survive as a satellite or sink to the center of the dominant galaxy to increase its mass. The binary interactions (fly-by and merging), among satellite subhalos, are  also described by the model. In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}. The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulating star formation (as well as BH accretion). The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase. A Salpeter IMF is adopted in the SAM simulation.

@@

\subsubsection{Illustris}
The Illustris Project is a serise of larger-scale hydrodynamical simulations of galaxy formation which was introduced in~\citet{2014MNRAS.444.1518V, 2014Natur.509..177V}. The simulation consist of a volume of (106.5 cMpc)$^3$, and was run with the moving Voronoi mesh code {\tt Arepo}~\citep{2010MNRAS.401..791S}. Besides gravitational force and hydrodynamical fluxes, the simulation calculates the astrophysical process known to be crucial for galaxy formation~\citep{2013MNRAS.436.3031V, 2014MNRAS.438.1985T}, which includes gas cooling, a subresolution ISM model, stochastic SF with a density threshold of 0.13 cm$^{-3}$, stellar evolution, gas recycling, chemical enrichment, kinetic stellar feedback by SNe activity, BH activity (accretion and merging), and AGN feedback. A cosmological background consistent with WMAP9~\citep{2013ApJS..208...19H} and a Chabrier IMF is adopted.

@@

\subsubsection{IllustrisTNG}
{\it The Next Generation Illustris Simulations} (IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018} are an ambitious suite of hydrodynamical simulations of galaxy formation in large cosmological volumes. It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modelling, and 3) addressing the identified shortcomings of the previous generation simulations.

@@

\subsubsection{Horizon-AGN}
The simulation of Horizon-AGN~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D} has a volume of (142 cMpc)$^3$ which was generated based on the adaptive mesh refinement code {\tt Ramses}~\citep{2002A&A...385..337T} with a $\Lambda$CDM model based on WMAP7~\citep{2011ApJS..192...18K} cosmological results. The total volume contains $1024^3$ DM particles, corresponding to a DM mass resolution of $8 \times 10^7  M_{\odot}$  and initial gas resolution of  $1\times10^7M_{\odot}$. A Salpeter IMF is assumed in Horizon-AGN simulation.

@@

\section{Comparison and Results} \label{sec:result}
\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.45\textwidth]{HSC_selection_MBII.png}} &
{\includegraphics[width=0.45\textwidth]{HST_selection_MBII.png}}
\end{tabular}
\caption{\label{fig:selection} 
{\it left}: The correlation between the \mbh\ and $L_{\rm bol}$ of the HSC sample is used to set the selection window for the simulated samples. This region roughly bracket the type-1 AGN sample. Taking MBII as example, the light green background cloud shows the simulated number density after added random uncertainty of the overall sample. 
{\it right}: Similar to the top plane -- equivalent selection window adopted for the HST-observed and MBII simulated samples.
}
\end{figure*}

To make direct comparison, we adopt the measurement error and the selection effect and apply to the simulation sample. To this end, we first inject random noise to the simulation catalog to mimic the scatter that caused by the measurement error. As mentioned in pervious section, the \smass\ and \mbh\ for HSC and HST samples are estimated by using the similar approach, and thus their uncertainty level is expected to be the same. 
We assume the following measurement uncertainties to add the random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.17~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
